---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nemsr

<!-- badges: start -->
[![R-CMD-check](https://github.com/byu-transpolab/nemsr/workflows/R-CMD-check/badge.svg)](https://github.com/byu-transpolab/nemsr/actions)
<!-- badges: end -->

The goal of nemsr is to enable researchers to quickly calculate NEMS-S scores 
for individual grocery stores using a Qualtrics-based NEMS-S survey developed
at BYU.

## Installation

<!--
You can install the released version of nemsr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("nemsr")
```
-->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("byu-transpolab/nemsr")
```

## Example

The NEMS-S data should come from a Qualtrics survey collected by a trained
surveyor. Download the data from Qualtrics in the `.sav` format (for SPSS).
Then you can read the data into R with the `read_nemss` function.

```{r read}
library(nemsr)

## basic example code
file <- system.file("extdata", "example_nems.sav", package = "nemsr")
(nemss <- read_nemss(file))
```

Once the data are in your R session, there are two basic things you might
like to do with them: a NEMS-S score and a market basket score.

### NEMS-S Score

The `calculate_nems_score()` function 

```{r scores, eval = FALSE}
calculate_nems_score(nemss)
```

### Market Basket

The `calculate_market_basket()` function computes the cost of a common market
basket at that store using the pricing data available weighted according to the
[Thrifty Food Plan, 2021](https://fns-prod.azureedge.us/sites/default/files/resource-files/TFP2021.pdf)

```{r pressure, echo = FALSE}
(basket_score <- calculate_market_basket(nemss))
```

For details on this function, its methods, and return information, see `?calculate_market_basket()`


